Analysis of Global Crises and Their Impact on Interational Well-Being

### 2024-11-15 Draft.Rmd
moved package loading to top

```{r initial_setup, include=FALSE}
# echo = FALSE will set the Rmd to *not* show the R code. Don't change this.
# You may change the default figure width and figure height as you please.
knitr::opts_chunk$set(echo = FALSE, message = FALSE, fig.width = 6)
# Put any libraries that you need to load here.
# DO NOT PUT "install.packages()" IN AN RMD FILE!!!
library(tidyverse)
library(arrow)
library(maps)
library(tinytex)
library(sf)
library(rnaturalearth)
library(corrplot)
library(scales)
library(geosphere)
library(ggridges)
```

@@

```{r summary_stats, fig.height=4, fig.width=6,}
library(gtsummary)
library(gapminder)

insight_2_sum_stats <- covid_happiness |> group_by(continent) |> select(continent, perceptions_of_corruption, total_cases) |> 
  tbl_summary(by = continent)
insight_2_sum_stats
```

>>>>

```{r initial_setup, include=FALSE}
# echo = FALSE will set the Rmd to *not* show the R code. Don't change this.
# You may change the default figure width and figure height as you please.
knitr::opts_chunk$set(echo = FALSE, message = FALSE, fig.width = 6)
# Put any libraries that you need to load here.
# DO NOT PUT "install.packages()" IN AN RMD FILE!!!
library(tidyverse)
library(arrow)
library(maps)
library(tinytex)
library(sf)
library(rnaturalearth)
library(corrplot)
library(scales)
library(geosphere)
library(ggridges)
library(gtsummary)
library(gapminder)
library(glue)
```

@@

```{r summary_stats, fig.height=4, fig.width=6,}
insight_2_sum_stats <- covid_happiness |> group_by(continent) |> select(continent, perceptions_of_corruption, total_cases) |> 
  tbl_summary(by = continent)
insight_2_sum_stats
```
